Active learning for efficient systematic reviews

### 2020-05-14 manuscript/manuscript/manuscript.Rmd
update paths

<!-- Active learning for detecting relevant publications - evaluating models across systematic reviews from different research areas.  -->

<!-- Evaluating active learning models across research contexts.  -->

<!--  generalizability  -->
<!-- --- -->
<!-- title: Manuscript drafts -->
<!-- author: "Gerbrich Ferdinands" -->
<!-- date: '`r format(Sys.time(), "%d %B, %Y")`' -->
<!-- output: -->

@@

\linenumbers
<!-- # Abstract -->
<!-- #### Background  -->
<!-- <!-- This study aims to contribute to this growing area of research by exploring  -->

<!-- #### Methods -->
<!-- <!-- A convenience sample of 5 existing systematic reviews on varying topics was collected. -->

<!-- #### Results -->
<!-- #### Conclusions -->

<!-- Besides time-consuming, the process of title and abstract screening is prone to human error [@Wang2020]. -->
<!-- (14 to 77,910, trimmed mean 1,286).  -->
<!-- Need to be screened by multiple researchers.  -->

# Background
Systematic reviews are top of the bill in research. A systematic review brings together all studies relevant to answer a specific research question [@PRISMA-PGroup2015]. Systematic reviews inform practice and policy [@Gough2002] and are key in developing clinical guidelines [@Chalmers2007]. However, systematic reviews are costly because they involve the manual screening of thousands of titles and abstracts to identify publications relevant to answering the research question.

@@

|    __RQ1__ What is the performance of several active learning models across different classification techniques?
|    __RQ2__ What is the performance of several active learning models across different feature extraction strategies? 
|    __RQ3__ Does the performance of active learning models differ across systematic reviews from different research areas?
<!-- is effective but rather simplistic as it is solely based on the relative frequency of words in the texts, the ordering of words in the texts cannot be taken into account.  -->
<!-- . yet rather simplistic as they cannot take into account the structure of the texts -->
<!-- the effect of adopting a different, more sophisticated strategies has not been investigated t -->
<!-- previous another model component worth exploring is the feature extraction strategy,  T It is worth evaluating strategies  -->
<!-- It  rather simplistic. Paragraph vector. As various feature extraction strategies exist, it is worth evaluating the different strategies as well. as mentioned by [@Yu2018] -->
<!-- many facets of models  -->
<!-- Previous studies adopt ...  -->
<!-- little attention has been paid to [@Yu2018] mention paragraph vector -->
<!-- How to represent  -->
<!-- the representation of the title an abstracts   -->
<!-- whilst there exists a  of classification techniques for an active learning model to adopt, research to date has confined to models adopting one classification strategy [@Yu2018; @Yu2018; @Miwa2014; @Wallace2010]. Models adopting other classification techniques have not been investigated.  -->
 <!-- evaluated techniques other than Support Vector Machines (SVM) -->
<!-- Although important issues in the application of active learning models on title and abstract screening have been addressed prior studies -->

<!-- on the reviewers screening decision ('relevant', 'irrelevant'), the model can incrementally improve its relevancy predictions on the remaining publications, and again select the next publication to be screened.   -->

<!-- The latest state-of-the-art methods implement active learning, where the model improves  -->
<!-- The algorithm aims to compute which papers in the pool need to be excluded and which need to be included, based on the reviewers decisions.  -->

<!-- The algorithm aims to detect whether a given publication is relevant or irrelevant to the systematic review and reorders the publications by their likeliness of relevance; the reviewer sees most relevant papers first!  -->
<!-- thereby its predictions can be  is allowed to choose the data points it would like to learn from, thus allowing it to learn more efficiently.  -->
<!-- Active learning systems attempt to overcome the labeling bottleneck by asking -->
<!-- queries in the form of unlabelled instances to be labelled by an oracle (e.g., a human -->
<!-- annotator). -->
<!--  that a machine learning algorithm can perform better with less training if it is allowed to choose the data from which it learns. An active learner may pose "queries," usually in the form of unlabelled data instances to be labelled by an "oracle" (e.g., a human annotator) that already understands the nature of the problem -->
<!-- in which a model can choose the data points it would like to learn from, thus allowing it to learn more efficiently -->
<!-- its predictions by interactively querying the user to provide labels to unlabelled data .  -->
<!-- In title and abstract screening this means that the active learning -->
<!-- is allowed to improve its predictions by choosing the data it wants to learn from.  -->

<!-- Although the effectiveness of active learning models in reducing workload in title and abstract screening has been extensively studied,  -->

@@

<!-- We demonstrate effectiveness of a generic/flexible tool for assisting researchers in the screening phase..? -->
<!-- To allow comparison of different models they need to be applied on the same dataset.  -->

<!-- "Screening is performed in two steps, first preliminarily based on title and abstract, -->
<!-- then based on full-text."  -->

<!-- add: current consensus active learning are state of the art: how do they woroK; by prioritizatio (put in a picture)  -->

<!-- #### identifying the niche  -->

<!-- By evaluating different configurations of an active learning model on different review contexts.  -->
<!-- status quo: prioritization + active learning? + certainty [@Miwa2014], but classifier  -->
<!-- Although several studies attempt to evaluate such methods,  -->
<!-- It makes  -->
<!-- although  tackle issues in the (complex) area,  -->
<!-- Furthermore, few studies have investigated the use of different classifiers in any systematic way -->
<!-- AI-aided title and abstract screening has been proven succesful in reducing workload, but a lack of replication and  -->

<!-- Furthermore, a comparison mode in public health and clinicial medicing [@Miwa2014] compared different classifier on different datasets and found differential performance on 'messier' social sciences datasets.   -->

<!-- #### Occupying -->
<!-- ##### (listing purpose of new research,  -->

<!-- The tool is generic such that any researcher can adjust modules to increase efficiency in this field.   -->
 <!-- [@OConnor2019] -->

<!-- ##### listing questions,  -->
<!-- This study .  -->
<!-- research questions:  -->
<!-- RQ1 – how -->
<!-- -	RQ1a – does classifier performance vary over different research areas? -->
<!-- (in what terms does it perform best)  -->

<!-- ASReview aims to reduce workload in the citation screening process by prioritizing the most relevant abstracts.  -->
<!-- ASReview combines in text classification  -->

<!-- Furthermore, this study makes a contribution to ...  by demonstrating a reproducible and flexible tool,  -->
<!-- Furthermore, a generic and reproducible workflow is presented to facilitate, hopefully to increase acceptability and usability by researchers performing systematic reviews.  -->

@@

<!-- Active learning for screening prioritization denotes the scenario in which the reviewer is labeling references that are presented by a machine learning model. The machine learning model learns from the reviewers' decision and uses this knowledge in selecting the next reference that will be presented to the reviewer. -->

<!-- - then active learning cycle starts in which the user makes a decision after each iteration of the model which is then used to re-train the model. -->

<!-- - instance $x$, label $y$ -->
<!-- - utility measure $\phi_A(\cdot)$ -->
<!-- - $x^*_A$ best query instance according to $\phi_A(\cdot)$ -->

<!-- The reviewer starts labeling some instances in $\mathcal{U}$, creating labelled data set $\mathcal{L}$. -->
<!-- This is the starting point for the active learning model. -->
<!-- The model trains a classifier who predicts ...  -->
<!-- The reviewer and the are interacting in the active learning cycle. -->
<!-- Based on previous labelling decisions by the reviewer, the model constantly reorders the remaining publications in the dataset. -->
<!-- meaning the reviewer the reviewer screens as little as possible while inclusion rate = high (not true but is nice statistic?) -->
<!-- The model is balancing two goals: obtain all relevant publications with as little as reviewing possible. -->
<!-- Active learning for screening prioritization denotes the scenario in which the reviewer is labeling references that are presented by a machine learning model. The machine learning model learns from the reviewers' decision and uses this knowledge in selecting the next reference that will be presented to the reviewer. -->
<!-- #### Assumptions  -->
<!-- 1) decisions of the original SR are **ground truth** (benchmark) (oracle) -->
<!-- study assumptions: -->
<!-- - simulation mode  -->
<!-- - assumptions (prior knowledge etc, oracle = reviewer). -->

<!-- A SR can be divided into phases.  -->
<!-- Everything starts with a **systematic search**, leading to -->
<!-- then citation screening is performed, then full-text screening -->
<!-- [@PRISMA-PGroup2015] -->

<!-- Selecting papers is a two-step process: abstract & fulltext screening -->
## Class imbalance problem
There are two classes in the dataset: relevant and irrelevant publications. Typically, the inclusion rate is low as only a fraction of the publications belong to the relevant class (2.94%, [@Borah2017]). The class imbalance causes the classifier to miss relevant publications, because there are far fewer examples of relevant than irrelevant publications to train on [@OMara-Eves2015]. Moreover, classifiers can achieve high accuracy but still fail to identify any of the relevant publications [@Wallace2010]. This is evident in the case of a systematic review dataset where only three percent of publications are relevant. A model would achieve 97% accuracy when classifying all publications as irrelevant, even though none of the relevant papers would have been correctly identified.

@@

 <!-- Logistic models the posterior directly, naive bayes has higher bias but lower variance,  -->
 <!-- logistic might perform better when trainign set increases. [@Ng2002] -->
<!-- To carry out classification of publications, a classifier takes given input features $\mathbf{X}$ -->
<!-- The model utilizes features of previously labelled publications and  -->
<!-- The model utilizes L to predict labels for all abstracts (classifier). (training) -->
<!-- a new paper is selected (query) the one that is most likely to be relevant. & queried  -->
<!-- The reviewer is asked to label the query (relevant, irrelevant), which is then added to the training set.  -->
<!-- Now the model can update in (retraining) its predictions based on the new training dataset. This is caled retraining.  -->
<!-- The cycle starts over again..  -->
<!-- As the cycle repeats itselfs, labelled dataset grows, predicitons improve hopefully and soon (or sooner than at random) the relevant publications will we identified. s -->
<!-- We want to classify based on some features from the instances $x$, feature vector $\mathbf{X}$.  -->

@@

<!-- Miwa et al. found that active learning was more difficult on data from the social sciences compared to data from the medical sciences and were able to link this difficulty to a natural difference in text complexity between these research areas [@Miwa2014]. As the study by Miwa et al. adopted a bow approach [@Miwa2014], we hypothesize that a more sophisticated feature extraction strategy has the potential to bridge the performance gap between these research areas.  -->

@@

<!-- most equipped to the current scenario in which we are dealing with highly imbalanced datasets and where the goal is to identify all relevant publications as soon as possible. -->

@@

## Set-up
<!-- The seven models consist of the components described in the Technical Details section, adopting four different classification techniques and two different feature extraction strategies:  -->

To address __RQ1__, four models combining every classifier with TF-IDF feature extraction were investigated:

@@

This study has been approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendment under study 20-104. Simulations were run in ASReview, version 0.9.3 [@ASReview2020]. Analyses were carried out using \texttt{R}, version 3.6.1 [@RCoreTeam2019]. Scripts and data are stored in the GitHub repository for this thesis^[https://github.com/GerbrichFerdinands/asreview-thesis].The output resulting from the simulation was stored on the Open Science Framework page of this thesis ^[https://osf.io/7mr2g/], as their size exceeded the storage limit of GitHub by far. Due to their large number, the simulations were carried out on Cartesius, the Dutch national supercomputer. Access was granted by SURF via a grant (ID EINF-156). 
<!-- can retrieve the labels from the annotated dataset instead -->
<!-- The oracle is not the reviewer but the labels in the data.  -->
<!-- The researcher has some prior knowledge about the pool, some papers ought to be included in the SR.  -->

<!-- Data are available via the $\texttt{ASReview}$ GitHub page^[https://github.com/asreview/systematic-review-datasets]. -->
<!-- All datasets accompanying the systematic reviews are openly published.  -->
## Datasets 
The models were simulated on a convenience sample of six systematic review datasets. The data selection process was driven by three factors. Firstly, datasets were selected based on their background, given the need for datasets from diverse research areas. Secondly, datasets were selected by their availability, given the limited timespan of the current project. Thirdly, all original data files should be openly published with a CC-BY license, and are available through the [$\texttt{ASReview}$ GitHub page](https://github.com/asreview/systematic-review-datasets).

@@

<!-- FN are far more problematic/unwanted/detrimental than FP: a researcher can label the FP as irrelevant whereas the FN are possibly never seen thereby missing relevant studies running the risk of an invalid systematic review.  -->
<!-- The goal is twofold: we want to identify all relevant papers, as fast as we can.  -->
<!-- Tradeoff: identifying all relevant papers and reducing workload.  -->
<!-- what about class imbalance.  -->

<!-- $$\texttt{WSS} = \frac{TN + FN}{N} - (1- recall) $$  -->
<!-- $$\texttt{ATD} = \frac{L}{N}$$ -->
<!-- $$\texttt{ATD} = \frac{L(relevant) }{N}$$ -->

<!-- Is performance related to some characteristic (n, inclusion rate, ...) -->

<!-- ? How to compare outcomes of 3 different optimization strategies?  -->

<!-- The cost of a false negative outweighs the cost of a false positive.  -->
<!-- Note that we assume the oracle/original user to hold the truth.  -->
<!-- This is of course not always the case.  -->
<!-- There are two classes in the data: exlusions and inclusions. -->

<!-- Datasets from the medical and social sciences, software engineering and public administration.  -->
<!-- Medical sciences SRs are viewed as more 'strict'/'structured' and social sciences more messy.  -->
<!-- Models are evaluated by performing a simulation on data from six existing systematic reviews from various research areas. -->
<!-- ### Optimizing hyperparameters -->
<!-- Every model component contains hyperparameters, leading to a unique set of hyperparameters for each model. To maximize model performance, we need to find optimal values for the hyperparameters.  -->
<!-- For every model the optimal hyperparameter values are determined by optimizing on the data $d$. -->
<!-- The hyperparameters are optimized by running several hundreds of optimization trials, in which hyperparameter values are sampled from their possible parameter space. -->
<!-- A description of all hyperparameters and their sample space can be found in the appendix.  -->
<!-- Maximum model performance is defined as the average time it takes to find an inclusion in the data, or more specific: the loss function minimizes the average number of papers needed to screen to find an inclusion (e.g. the area above the curve in the inclusion plot). -->

<!-- The optimization data $d$ consists of (a subset from) the six systematic review datasets $D$ mentioned above.  -->
<!-- Three different approaches in composing $d$ are explored:  -->

<!-- - __one__, where hyperparameters are optimized on only one of the six datasets, $d \in D$. Such hyperparameters are expected to lead to maximum performance in the same dataset $d$. -->
<!-- - __n__, where hyperparameters are optimized on all six data sets, $d = D$. This optimization approach intends to serve in producing the most optimal hyperparameters overall.  -->
<!-- - __n-1__, where hyperparameters are optimized on all six datasets but one, $d \subset D$. Serving as a sensitivity analysis for the former condition, e.g. how sensitive are the hyperparamters. also as a cross-validation later on: hyperparameters obtained by training data, test data is never seen before. -->
<!-- where d are all datasets but the one where we want to simulate later on.  -->
<!-- This results in $6+6+1=13$ sets of hyperparameters for every model.  -->

<!-- Results were visually inspected to check if an optimum (minimal loss) has been reached.  -->
<!-- More trials were run if the loss still seemed to go down at a quick pace.  -->

<!-- The hyperparameter values that were found to lead to a minimum loss value were visually inspected.  -->

<!-- \newpage -->
<!-- ## Background -->
<!-- [@Yu2018], [@Yu2018] simulated 32 svm classifiers, on software engineering.  -->
<!-- A popular classifier is SVM. succes with HUTM (fastread), uncertainty, mix of weighting and agressive undersampling,  -->
<!-- In terms of Yu et al, we adopt .CT.  -->

<!-- SVM - tf-idf on medical data, uncertainty sampling, agressive undersampling. [@Wallace2010]  -->

<!-- abstrackr svm certainty  -->

<!-- SVM + Weighting + uncertainty (bow) produced good methods  [@Miwa2014] -->
<!-- Also include social sciences data besides medical data.  -->

<!-- [@Cohen2006] perceptron-based classifier (neural network)  -->

<!-- SVM on legal documents (no balancing, certainty ) [@Cormack2014]  -->
<!-- in limitations section mentions that LR yields about same results, nb inferior results.  -->

<!-- [@Kilicoglu2009] - SVM, naive bayes, boosting and combinations. future work should optimize parameters. -->
<!--   "Regarding the base classifiers used in identifying method- ologically rigorous studies, boosting consistently strikes the best balance between precision and recall, whereas naive Bayes in general performs well on recall (demonstrating a tradeoff between recall and precision), as does polynomial SVM on precision. The AUC results are mixed, although boosting has a slight edge overall. These results demonstrate that different classifiers can be used to satisfy different information needs (SVM for specificity, naive Bayes for sensitivity, and boosting for balance between the two, for example)." -->

<!-- Our extensions is that we try different classifiers, on more datasets.  -->

<!-- When no balancing is applied, the training data set = labelled data set $\mathcal{L}$ -->
<!-- The model can query the labels, who serve as the reviewer, active learning then perform active learning to detect inclusions. -->

<!-- a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy.  -->
<!-- Using a perceptron classifier, WSS@95% = 56.61 in [@Cohen2006]. (5x2 crossvalidation). Can we beat this?  -->
<!-- The data -->

<!-- Openness, reproducible,  -->

<!-- Benefits:  -->

<!-- Adopting some sort of stopping criterion (outside scope of the current thesis) the reviewer can quit reviewing after having read only a fraction of candidate studies.  -->
<!-- meaning the screening process can be finished after reading a fraction of all candidate studies. Saving hours of time and resources.  -->

<!-- paper organization: -->

<!-- The goal is to gain insight in classifiers other than the widely applied SVM, overall various research areas.  -->
<!-- So not only medical sciences.  -->

<!-- Although considerable research has been devoted to ..., less attention has been paid to the comparison of different classifiers.  -->
<!-- Few studies have evaluated different classifiers in any systematic way -->
<!-- different models to use haven't been investigated in a systematic way (only in software engineering) -->

<!-- 1) the lack of replication of methods is making it impossible to draw any overall conclusions about best practice/ best approaches of the problem of reducing workload in screening.  -->
<!-- 2) screening prioritization is appealing to systematic reviewers because ... -->
<!-- 3)  -->
<!-- 4) implemantation: usabliity and acceptability of such tools amongst researchers conducting a systematic review.  -->

<!-- lack of studies investigating the effect of different methods over different research areas. (yu but only software engineering, miwa perhaps?) -->
<!-- There is also a significant lack of examples outside of healthcare with the exception of one example in software engingeering  -->

<!-- However, there is a need for consensus () and transparancy?  -->

<!-- So far, however, there has been little discussion about the different classifiers to be used. Support Vector Machine has been the default in almost all studies.   -->

<!-- Several algorithms to assist the reviewer in the abstract screening process have been proposed. (they are available in many shapes/sorts).  -->

<!-- <!-- RQ2 different hyperparameter optimizations? --> 
<!-- <!-- Classifiers come with hyperparameters. We have to make a choice on how to set these hyperparameters. What we do is create 3 sets, optimizing in three ways, aggregate results obtained.   -->

<!-- For truly evaluate the effectiveness of such methods,  -->

<!-- Such a solution can save time and resources. Time saving is not the only benefit: and help to minimize bias..  -->

<!-- #### Proposed solution -->
<!-- This study is about how machine learning models can increase efficiency in systematic reviews. -->
<!-- Their main objective is to identify ..  -->

<!-- The strategy to reduce workload proposed in the current study is by prioritizing publications that are deemed most relevant to the systematic review.  -->
<!-- As the relevant publications are screened first, the reviewing process can be quit earlier.  -->

<!-- The stage of abstract screening where abstracts are systematically screened is where a lot is to be gained. This stage is the target of possible learning algorithms that can assist the reviewer in selecting the relevant papers. Together with the reviewer /human machine interaction.  The algorithm aims to compute which papers in the pool need to be excluded and which need to be included, based on the reviewers decisions. It learns from the reviewers decisions and asks the reviewer to provide more labels, incrementally improving its class predictions.  -->

<!-- The goal of the algorithm defined in the current study is to reduce to number of abstracts needed to screen (maybe not right term, bit biomedical). To be more specific, the algorithm aims to present the reader with the primary studies as soon as possible. This means that at some point you probably have seen all relevant abstracts and are only viewing excluded papers, which means you can stop reviewing much earlier (theoretically spoken). Also reviewing is now much more fun. As compared to when you have to review all abstracts and you perhaps see only one relevant abstract every other week/day.  -->

<!-- ### Background -->
<!-- ... starts with a search for potentially relevant publications.  -->
<!-- This initial set of candidate studies need to be manually screened to identify the publications relevant for answering the research question.  -->
<!-- Because the initial set often consists of thousands of papers and the -->

<!-- To gather the findings relevant to answering the research question, a systematic search is performed. -->
<!-- A systematic search starts with collecting all publications that meet pre-specified eligibility criteria. -->
<!-- From this collection of candidate studies the researcher has to identify the publications relevant for answering the research question.  -->
<!-- Of all candidate studies only a fraction is relevant [...].  -->
<!-- As more and more papers are published and reproducibility crisis has emerged,  -->
<!-- A systematic search often results in thousands of candidate studies. -->
<!-- Relevant publications are then identified by screening title and abstract of all candidate studies.  -->
<!-- This screening process is a manual task often executed by multiple reviewers to ensure reliability.  -->
<!-- This is a time consuming process that weighs heavily on resources.  -->

<!-- Most often the SVM classifier is used, popular and very good results. Also lots of other configurations. However, other classifiers have not been tested a lot (polygon thing by cohe, naïve bayes and random forest by …), but mostly SVM still. Also, most research in the medical sciences (well there are some exceptions of course [conversation between cohen and matwill]  -->

<!-- A solution is ...  -->

<!-- It is important reflect on research by giving an overview of research areas which is typically done by a systematic review […].  -->

<!-- To review a specific research area, one starts out with an initial search of thousands of academic papers. All these papers abstracts need to be screened to find an initial batch of possibly relevant papers. With now hopefully only a couple of hundred papers left, the researcher needs to read these papers full-text to arrive at a final selection of papers that are relevant for the final systematic review [this is prisma process?]. This whole processes costs this and this much time [shelmilt].  -->

<!-- ----  -->

<!-- ## active learning for systematic reviews  -->
<!-- corpus = all the text:  -->

<!-- Active learning =  -->
<!-- increasing classification performance with every query.  -->
<!-- The query strategy determines the way unlabelled papers are queried to the researcher.  -->

<!-- [@modAL2018] -->

<!-- \newpage -->

<!-- ### Optimization results -->
<!-- For every model, 13 sets of hyperparameters were optimized. -->

<!-- *to include: plotting the loss reduction over trials*  -->

<!-- Optimal values of the hyperparameters were visually inspected. -->

<!-- As an example, the hyperparameters of the RF_TF-IDF model are presented in Figure 1.  -->
<!-- A panel displays the optimal values for a certain hyperparameter, where the blue colored dots represent the __one__ condition, the green dots the __n-1__ condition and the orange dot represents the optimal hyperparameter value when optmizing over all datasets (__n__). The x-axis represents the possible parameter space where the vertical grey lines mark the boundaries of the hyperparameter space (if possible). Note that the feature parameters ngram_max, split_ta, use_keywords and model parameters max_features and n_estimators are categorical.  -->

<!-- Overall, the optimal values are distributed over the parameter space. Outlying values all belong to the __one__ condition where optimization was dependent on one dataset only. Fore example, the class_weight parameter has an outlying value of 11.3 that belongs to the nudging dataset. (Why this is the case I can only speculate, but it is worth mentioning that this dataset has a relatively high inclusion rate  of 5.41%, compared to the other datasets).  -->

<!-- ```{r} -->
<!-- include_graphics( -->
<!--   "figs/rf_tfidf.eps", -->
<!-- ) -->
<!-- ``` -->

<!-- ## Appendix x - Hyperparameters and their sample space  -->

<!-- Classifier hyperparameters -->

<!--     class_weight: normal(0,1) constrained to be > 0 -->
<!--     class weight of the inclusions. -->

<!--   Logistic Regression -->

<!--     c: float. normal(0,1), constrained to be > 0 -->

<!--   Support Vector Machine -->

<!--     gamma: ["auto", "scale"], -->
<!--     Gamma parameter of the SVM model. -->

<!--     C:  -->
<!--     C parameter of the SVM model. -->

<!--     kernel: -->
<!--     SVM kernel type.["linear", "rbf", "poly", "sigmoid"] -->

<!--   Naive Bayes -->

<!--     "model_param.alpha", # exp(normal(0,1)) -->

<!--   Random Forest  -->

<!--     max_features: int (between 6 and 10) -->
<!--         Number of features in the model. -->

<!--     n_estimators: int between 10 and 100  -->
<!--         Number of estimators. -->

<!--     model_param.n_estimators" #quniform(10,100,1) -->

<!-- Balance strategy hyperparameters: -->
<!--     Dynamic supersampling: -->

<!--     a: float -->
<!--         Governs the weight of the 1's. Higher values mean linearly more 1's -->
<!--         in your training sample. -->
<!--     alpha: float -->
<!--         Governs the scaling the weight of the 1's, as a function of the -->
<!--         ratio of ones to zeros. A positive value means that the lower the -->
<!--         ratio of zeros to ones, the higher the weight of the ones. -->
<!--     b: float -->
<!--         Governs how strongly we want to sample depending on the total -->
<!--         number of samples. A value of 1 means no dependence on the total -->
<!--         number of samples, while lower values mean increasingly stronger -->
<!--         dependence on the number of samples. -->

<!-- Feature extraction strategy hyperparameters -->

<!--     split_ta: 0 or 1 -->
<!--        whether titles and abstracts are split  -->

<!--     use_keywords: 0 or 1 -->
<!--         whether keywords should be used -->

<!--   TF-IDF -->

<!--     ngram_max: 1, 2 or 3 -->
<!--         Can use up to ngrams up to ngram_max. For example in the case of  -->
<!--         ngram_max=2, monograms and bigrams could be used. -->

<!--   Doc2Vec -->

<!--     vector_size: int (between 32 and 127) -->
<!--         Output size of the vector. -->

<!--     epochs: int (between 20 and 50) -->
<!--         Number of epochs to train the doc2vec model. -->

<!--     min_count: int (between 1 and 3) -->
<!--         Minimum number of occurences for a word in the corpus for it to be  -->
<!--         included in the model. -->

<!--     window: int (between 5 and 9) -->
<!--         Maximum distance over which word vectors influence each other. -->

<!--     dm_concat: int 0 or 1 -->
<!--         Whether to concatenate word vectors or not. -->

<!--     dm: int  -->
<!--         Model to use. -->
<!--         0: Use distribute bag of words (DBOW). -->
<!--         1: Use distributed memory (DM). -->
<!--         2: Use both of the above with half the vector size and concatenate them. -->

<!--     dbow_words: int 0 or 1 -->
<!--         Whether to train the word vectors using the skipgram method. -->

<!-- # The software  -->
<!-- ASReview takes the following parameters/arguments:  -->
<!--  We now have 75 combinations.  -->
<!-- for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed. From these $5*5*3=75$ simulation studies, performance of the different models is evaluated. -->

@@

<!-- although the RF + TF-IDF model performs seems to be the lowest performing model for the longest part of the screening process.   -->
<!-- , buy the SVM + D2V model (pink) reaches this point of 95% recall earlier than the LR + TF-IDF model (yellow).  -->

@@

```{r, eval = TRUE, fig-sub-nudging, fig.cap = "Recall curves for the Nudging dataset. ", fig.subcap=c('All seven models',  "Models adopting TF-IDF feature extraction", "Models adopting D2V feature extraction",'D2V vs TF-IDF for LR classifier', 'D2V vs TF-IDF for RF classifier', "D2V vs TF-IDF for SVM classifier")}
# path
# nudgingplots <- list.files("/Volumes/Gerbrich/asreview/results/one_seed/plots/nudging", full.names=TRUE)
f <- c("inclusion_all_nudging", "inclusion_tfidf_nudging", "inclusion_d2v_nudging", "inclusion_d2v_vs_tfidf_logistic_nudging", "inclusion_d2v_vs_tfidf_rf_nudging", "inclusion_d2v_vs_tfidf_svm_nudging")
nudgingplots <- paste0("/Volumes/Gerbrich/asreview/results/one_seed/plots/nudging/", f, ".pdf")
include_graphics(nudgingplots)
```
<!-- is apparent that models adopting the TF-IDF feature extraction strategy are outperformed by their Doc2Vec-using counterparts:  -->
<!-- The best performing model in terms of ATD is NB + TF-IDF (9.25, 0.29), LR + TF-IDF (9.46, 0.19), SVM + TF-IDF (62.20),and RF + TF-IDF (11.6, 0.43). SVM + D2V (8.71, 0.33), LR + D2V (8.73, 0.47), RF + D2V (10.17, 0.88).  -->

@@

```{r, eval = TRUE, fig-sub-alldata, fig.cap = "Recall curves for all seven models on (a) the PTSD, (b) Software, (c) Ace, (d) Virus, and (e) Wilson dataset.", fig.subcap=c("PTSD","Software","Ace","Virus","Wilson")}
d <- c("ptsd", "software", "ace", "virus", "wilson")
files <- c("/Volumes/Gerbrich/asreview/results/one_seed/plots/ptsd/inclusion_all_ptsd.pdf" ,paste0("/Volumes/Gerbrich/asreview/results/one_seed/plots/", d[2:5], "/nolegend_inclusion_all_", d[2:5], ".pdf"))
include_graphics(files)
```

@@

plots <- paste0("/Volumes/Gerbrich/asreview/results/one_seed/plots/ptsd/", f, "ptsd.pdf")
include_graphics(plots)
```

## Software
```{r, fig-sub-software, fig.cap = "Recall curves for the Software dataset. ", fig.subcap=c('All seven models',  "Models adopting TF-IDF feature extraction", "Models adopting D2V feature extraction",'D2V vs TF-IDF for LR classifier', 'D2V vs TF-IDF for RF classifier', "D2V vs TF-IDF for SVM classifier") }
# path
plots <- paste0("/Volumes/Gerbrich/asreview/results/one_seed/plots/software/", f, "software.pdf")
include_graphics(plots)
```

>>>>

<!-- --- -->
<!-- title: Manuscript drafts -->
<!-- author: "Gerbrich Ferdinands" -->
<!-- date: '`r format(Sys.time(), "%d %B, %Y")`' -->
<!-- output: -->

@@

\linenumbers
# Background
Systematic reviews are top of the bill in research. A systematic review brings together all studies relevant to answer a specific research question [@PRISMA-PGroup2015]. Systematic reviews inform practice and policy [@Gough2002] and are key in developing clinical guidelines [@Chalmers2007]. However, systematic reviews are costly because they involve the manual screening of thousands of titles and abstracts to identify publications relevant to answering the research question.

@@

|    __RQ1__ What is the performance of several active learning models across different classification techniques?
|    __RQ2__ What is the performance of several active learning models across different feature extraction strategies? 
|    __RQ3__ Does the performance of active learning models differ across systematic reviews from different research areas?

@@

@@

## Class imbalance problem
There are two classes in the dataset: relevant and irrelevant publications. Typically, the inclusion rate is low as only a fraction of the publications belong to the relevant class (2.94%, [@Borah2017]). The class imbalance causes the classifier to miss relevant publications, because there are far fewer examples of relevant than irrelevant publications to train on [@OMara-Eves2015]. Moreover, classifiers can achieve high accuracy but still fail to identify any of the relevant publications [@Wallace2010]. This is evident in the case of a systematic review dataset where only three percent of publications are relevant. A model would achieve 97% accuracy when classifying all publications as irrelevant, even though none of the relevant papers would have been correctly identified.

@@

@@

@@

@@

## Set-up
To address __RQ1__, four models combining every classifier with TF-IDF feature extraction were investigated:

@@

This study has been approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendment under study 20-104. Simulations were run in ASReview, version 0.9.3 [@ASReview2020]. Analyses were carried out using \texttt{R}, version 3.6.1 [@RCoreTeam2019]. Scripts and data are stored in the GitHub repository for this thesis^[https://github.com/GerbrichFerdinands/asreview-thesis].The output resulting from the simulation was stored on the Open Science Framework page of this thesis ^[https://osf.io/7mr2g/], as their size exceeded the storage limit of GitHub by far. Due to their large number, the simulations were carried out on Cartesius, the Dutch national supercomputer. Access was granted by SURF via a grant (ID EINF-156).

## Datasets 
The models were simulated on a convenience sample of six systematic review datasets. The data selection process was driven by three factors. Firstly, datasets were selected based on their background, given the need for datasets from diverse research areas. Secondly, datasets were selected by their availability, given the limited timespan of the current project. Thirdly, all original data files should be openly published with a CC-BY license, and are available through the [$\texttt{ASReview}$ GitHub page](https://github.com/asreview/systematic-review-datasets).

@@

@@

@@

```{r, eval = TRUE, fig-sub-nudging, fig.cap = "Recall curves for the Nudging dataset. ", fig.subcap=c('All seven models',  "Models adopting TF-IDF feature extraction", "Models adopting D2V feature extraction",'D2V vs TF-IDF for LR classifier', 'D2V vs TF-IDF for RF classifier', "D2V vs TF-IDF for SVM classifier")}
# path
# nudgingplots <- list.files("../../results/one_seed/plots/nudging", full.names=TRUE)
f <- c("inclusion_all_nudging", "inclusion_tfidf_nudging", "inclusion_d2v_nudging", "inclusion_d2v_vs_tfidf_logistic_nudging", "inclusion_d2v_vs_tfidf_rf_nudging", "inclusion_d2v_vs_tfidf_svm_nudging")
nudgingplots <- paste0("../../results/one_seed/plots/nudging/", f, ".pdf")
include_graphics(nudgingplots)
```
<!-- is apparent that models adopting the TF-IDF feature extraction strategy are outperformed by their Doc2Vec-using counterparts:  -->
<!-- The best performing model in terms of ATD is NB + TF-IDF (9.25, 0.29), LR + TF-IDF (9.46, 0.19), SVM + TF-IDF (62.20),and RF + TF-IDF (11.6, 0.43). SVM + D2V (8.71, 0.33), LR + D2V (8.73, 0.47), RF + D2V (10.17, 0.88).  -->

@@

```{r, eval = TRUE, fig-sub-alldata, fig.cap = "Recall curves for all seven models on (a) the PTSD, (b) Software, (c) Ace, (d) Virus, and (e) Wilson dataset.", fig.subcap=c("PTSD","Software","Ace","Virus","Wilson")}
d <- c("ptsd", "software", "ace", "virus", "wilson")
files <- c("../../results/one_seed/plots/ptsd/inclusion_all_ptsd.pdf" ,paste0("../../results/one_seed/plots/", d[2:5], "/nolegend_inclusion_all_", d[2:5], ".pdf"))
include_graphics(files)
```

@@

plots <- paste0("../../results/one_seed/plots/ptsd/", f, "ptsd.pdf")
include_graphics(plots)
```

## Software
```{r, fig-sub-software, fig.cap = "Recall curves for the Software dataset. ", fig.subcap=c('All seven models',  "Models adopting TF-IDF feature extraction", "Models adopting D2V feature extraction",'D2V vs TF-IDF for LR classifier', 'D2V vs TF-IDF for RF classifier', "D2V vs TF-IDF for SVM classifier") }
# path
plots <- paste0("../../results/one_seed/plots/software/", f, "software.pdf")
include_graphics(plots)
```

## Ace
```{r, fig-sub-ace, fig.cap = "Recall curves for the Ace dataset. ", fig.subcap=c('All seven models',  "Models adopting TF-IDF feature extraction", "Models adopting D2V feature extraction",'D2V vs TF-IDF for LR classifier', 'D2V vs TF-IDF for RF classifier', "D2V vs TF-IDF for SVM classifier") }
# path
plots <- paste0("../../results/one_seed/plots/ace/", f, "ace.pdf")
include_graphics(plots)
```
